Title

### 2023-05-22 main.tex
fail

\begin{figure}
\centering
\begin{subfigure}{0.9\textwidth}
\begin{subfigure}{.666\textwidth}
\centering
\includegraphics[width=.95\columnwidth]{images/tetra-def.png}
\end{subfigure}%
\begin{subfigure}{.333\textwidth}
\includegraphics[width=.95\columnwidth]{images/corte1-2.png} \\
\includegraphics[width=.95\columnwidth]{images/corte2-2.png} \\
\end{subfigure}
\includegraphics[width=.322\columnwidth]{images/corte3-2.png}
\includegraphics[width=.322\columnwidth]{images/corte4-2.png}
\includegraphics[width=.322\columnwidth]{images/corte5-2.png}
\end{subfigure}%
\begin{subfigure}{0.1\textwidth}
\includegraphics[width=.8\columnwidth]{images/col-2.png} \\ [2ex]
\end{subfigure}
\caption{\cpnote{}\tbnote{Aquí está una forma alternativa en que puede quedar la figura. 
Usé $2(1-p_{succ})$ en lugar de $p_{succ}$ para que se cumpla lo de
que $0$ es lo peor y $1$ lo mejor.}}
\end{figure}

% }}}
% }}}
\section{One Parameter Circuits} % {{{
\label{sec: 1PR Circuits}
\cpnote{Quizá abrir con un parrafo de motivacion. Quizá lo tenemos que hablar. }
\cpnote{No se sabe aun que son 1PR circuits. Poner completo} \tbnote{Ya.}

Just as Pauli channels, Pauli dynamical maps can be implemented using the circuit
of \fref{fig: circuit-pauli}. However, there is one difference: 
the state to be created on the ancilla qubits now 
depends on a parameter $p$, and it is represented by the expression:
\begin{eqnarray}
\label{eq: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}
Thus, we temporarily shift our focus from Pauli
channels and dynamical maps to the general problem of 
creating a circuit to generate a curve of
states like the one described in \eref{eq: parametrized state}.
\cpnote{me gusta mas usar el comando eref para que si toca cambiarlo, dependiendo 
de la revista, lo pueda hacer de un solo jalon. Lo mismo para las 
figuras.} \tbnote{Ah va, lo puse en todas.}

In general, producing this curve of states will require multiple rotations
parametrized by $p$. For instance, in the case of a two-qubit curve of states,
we would typically need three rotations that depend on $p$, similar to those
illustrated for the ancilla qubits in \fref{fig: circuit-pauli-1}.
Moreover, creating an $N$-qubit curve of states
usually necessitates $2^N-1$ parametrized rotations.
\cpnote{no me salen esas cuentas.} \tbnote{Se me olvidaba el 2, ya está bien}

However, it is desirable to minimize the number of parametrized rotations in our circuit.
\cpnote{why?}
This leads us to the following question: which curves of states,
such as the one described in \eref{eq: parametrized state}, 
can be generated using only a single parametrized rotation? 
To clarify this, we provide the following definition for a circuit with one parametrized rotation.
\cpnote{Creo qeu los dos párrafos anteriores son uno y toca pensar cual es el
mensaje principal y rediseñar. }
\tbnote{De acuerdo, Lo cambié a esto:}

{\color{orange} In general, producing this curve of states for $N$ qubits will require
$2^N-1$ rotations parametrized by $p$,
such as the three rotations used for the ancilla
qubits in \fref{fig: circuit-pauli-1}.
However, it would be preferable to achieve the same effect using only one parametrized rotation. 
This would allow us to interpret said rotation 
as a knob that smoothly traverses the curve of states.
Consequently, we are faced with the question of which curves of states, 
such as the one described in \eref{eq: parametrized state}, 
can be produced using just a single parametrized rotation. 
To clarify this, we provide the following definition 
for a circuit with one parametrized rotation.}

@@

Based on this definition, we aim to determine which curves of 
states can be generated using 1PR \cpnote{Si te parece bien el cambio 
en la sigla, cambialos todos} 
\tbnote{Sí me parece, los cambié} circuits. 
To accomplish this, we begin by proving that all 1PR circuits have 
the form depicted in \fref{fig:1PR-circuit},
where the parametrized rotation is around $\sigma_3$ and
is applied to the last qubit.

\begin{figure} % {{{
\centering
\includegraphics{images/OPR-circuit.pdf}
\caption{\textbf{General form of a 1PR circuit}.
Any 1PR circuit can be transformed into this form,
where the rotation on the last qubit
can be controlled or not by any of the other qubits.
$A$ and $B$
are $N$-qubit gates that do not depend on the parameter $p$ and
$s= s(p)$ is a function of the parameter.
\cpnote{Parece que se te olvida la puntuacion en algunos captions. 
por otro lado, queda la figura a mitad de la prueba. A mi me gusta dejar 
que Latex organice solo las figuras y sin ponerle el h! ni nada. } \tbnote{Va}
}
\label{fig:1PR-circuit}
\end{figure} % }}}

@@

Next, we note that it is not necessary to consider rotations about an arbitrary axis,
as a rotation about any axis $\hat{n}$ parameterized by $p$
can be transformed into a rotation about $\sigma_3$ without introducing 
gates that depend on $p$. To see this, consider the rotation $R_{\hat{n}}(2s)$, where $2s$ 
is a function of $p$ (the factor of 2 is for convenience later on) 
and $\hat{n} = (n_1,n_2,n_3)$ represents the rotation axis. 
We can express $\hat{n}$ as $(\sin \theta \cos \phi, \sin \theta \sin \phi, \cos \theta)$, 
where $\theta$ and $\phi$ are fixed angles dependent on $\hat{n}$. 
The rotation can then be rewritten as follows:
\begin{eqnarray}
R_{\hat{n}}(2s) = R_{\sigma_3}(\phi) R_{\sigma_2}(\theta) R_{\sigma_3}(2s) R_{\sigma_2}(-\theta) R_{\sigma_3}(-\phi).
\end{eqnarray}
Since the angles $\theta$ and $\phi$ do not depend on the parameter $p$,
any 1PR circuit can be transformed into a circuit where the parametrized
 rotation is around $\sigma_3$ instead of an arbitrary axis. 
Moreover, without loss of generality, we can choose the last qubit as the
target qubit for the rotation \cpnote{Why?} 
{\color{orange} , since if it weren't, we could use
swap gates to move the rotation
to the last qubit without adding gates
that depend on $p$. }.

Therefore, a 1PR circuit can be transformed such
that the rotation is around $\sigma_3$ and is applied to the last qubit 
(possibly controlled by other qubits), 
resulting in the form depicted in \fref{fig:1PR-circuit}. 
\cpnote{Creo que este ultimo parrafo sobra, aunque hay detalles aca que quizá se pueden
poner en el planteamiento del problema.} \tbnote{Lo pasé arriba justo antes del teorema y quitaría este párrafo entonces }
$\blacksquare$ \\
$\;$\\

@@

First, applying $B$ to $|j\rangle$ results in $B|j\rangle = B_{0,j} |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$,
which can be rewritten by separating the
first $N-1$ qubits from the last one as:
\begin{equation}
B|j\rangle = \sum_{k=0}^{2^{N-1}-1} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j} |k\rangle |1 \rangle \right).
\end{equation}
After the operator $B$, the circuit applies the  controlled rotation $R$.
To simplify the analysis, we separate the states of
the first $N-1$ qubits into those that fulfill the control conditions of the rotation
(which we denote as the set $\mathcal{C}$)
and those that do not, and write it as
\begin{eqnarray}
B|j\rangle = \sum_{k \in \mathcal{C}} \left(B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j} |k\rangle |1 \rangle \right) + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j}|k\rangle |1\rangle \right),
\end{eqnarray}
Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
and not the others. Therefore,  
remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is}$ to $|0\rangle$
and a phase $e^{is}$ to $|1\rangle$, $RB|j\rangle$ is equal to:
\begin{small}
\begin{eqnarray}
&e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
+ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
& \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
\end{eqnarray}
\end{small}
where $\vec{a'} = \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle$, $\vec{b'}_j = \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle$, $\vec{c'}_j =\sum_{k \not\in \mathcal{C}} \big( B_{2k,j} |k\rangle |0\rangle+$ $ B_{2k+1} |k\rangle |j \rangle \big)$.
 These vectors are clearly orthogonal because they are each linear combinations of different 
orthogonal states of the computational base. 
Moreover, they satisfy $|\vec{a'}_j|^2 + |\vec{b'}_j|^2 + |\vec{c'}_j|^2 = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
which is unitary.

@@

%Therefore, from this theorem we conclude that
%the kind of curves of states that can be created
%using a 1PR circuit are always of the form
%\begin{align*}
%|b(p)\rangle= e^{is} \vec{a} + e^{-is} \vec{b} + \vec{c},
%\end{align*}
%where $s$ is a function of $p$, $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors and
%$|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2 = 1$.
%%\textbf{Puntos:}
%\begin{itemize}
%\item As said before, to implement a Pauli dynamical map, 
%we need to create the parametrized $2n$-qubit state 
%$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
%\item However, creating this state will in general require many rotations parametrized by $p$. 
%For example, for the case of a Pauli dynamical map on 1 qubit, 
%the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
%In general, to create a parametrized state on $2n$ ancilla qubits will require
%$2n-1$ rotations parametrized by $p$.
%\item How can we reduce the amount of parametrized rotations used?
%\item \textbf{1PR Circuit:} Define an 1PR circuit (a circuit with one parametrized rotation)
%\item \textbf{Theorem about 1PR circuits:} \textit{An 1PR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
%\begin{eqnarray}
%U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
%\end{eqnarray}
%\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
%\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
%aunque se puede y debe achicar bastante.
%\end{itemize}
\newpage
% }}}
\section{1PR circuit for a Pauli map} % {{{
\label{sec: 1PR circuit for a Pauli map}

>>>>

\begin{figure}
\centering
\begin{subfigure}{0.9\textwidth}
\begin{subfigure}{.666\textwidth}
\centering
\includegraphics[width=.95\columnwidth]{images/tetra-def.png}
\end{subfigure}%
\begin{subfigure}{.333\textwidth}
\includegraphics[width=.95\columnwidth]{images/corte1-2.png} \\
\includegraphics[width=.95\columnwidth]{images/corte2-2.png} \\
\end{subfigure}
\includegraphics[width=.322\columnwidth]{images/corte3-2.png}
\includegraphics[width=.322\columnwidth]{images/corte4-2.png}
\includegraphics[width=.322\columnwidth]{images/corte5-2.png}
\end{subfigure}%
\begin{subfigure}{0.1\textwidth}
\includegraphics[width=.8\columnwidth]{images/col-2.png} \\ [2ex]
\end{subfigure}
\caption{\cpnote{porfa escribe el caption.} \tbnote{Aquí está una forma
alternativa en que puede quedar la figura.  Usé $2(1-p_{succ})$ en lugar de
$p_{succ}$ para que se cumpla lo de que $0$ es lo peor y $1$ lo mejor.}}
\end{figure}

% }}}
% }}}
\section{One Parameter Circuits} % {{{
\label{sec: 1PR Circuits}

Just as Pauli channels, Pauli dynamical maps can be implemented using the circuit
of \fref{fig: circuit-pauli}. However, there is one difference: 
the state to be created on the ancilla qubits now 
depends on a parameter $p$, and it is represented by the expression:
\begin{eqnarray}
\label{eq: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}
Thus, we temporarily shift our focus from Pauli
channels and dynamical maps to the general problem of 
creating a circuit to generate a curve of
states like the one described in \eref{eq: parametrized state}.

In general, producing this curve of states for $N$ qubits will require
$2^N-1$ rotations parametrized by $p$\cpnote{De de donde sale este numero?},
such as the three rotations used for the ancilla
qubits in \fref{fig: circuit-pauli-1}.
However, it would be preferable to achieve the same effect using only one parametrized rotation. 
This would allow us to interpret said rotation 
as a knob that smoothly traverses the curve of states.
Consequently, we are faced with the question of which curves of states, 
such as the one described in \eref{eq: parametrized state}, 
can be produced using just a single parametrized rotation. 
To clarify this, we provide the following definition 
for a circuit with one parametrized rotation.

@@

Based on this definition, we aim to determine which curves of 
states can be generated using 1PR circuits. 
To accomplish this, we begin by proving that all 1PR circuits have 
the form depicted in \fref{fig:1PR-circuit},
where the parametrized rotation is around $\sigma_3$ and
is applied to the last qubit.

\begin{figure} % {{{
\centering
\includegraphics{images/OPR-circuit.pdf}
\caption{\textbf{General form of a 1PR circuit}.
Any 1PR circuit can be transformed into this form,
where the rotation on the last qubit
can be controlled or not by any of the other qubits.
$A$ and $B$
are $N$-qubit gates that do not depend on the parameter $p$ and
$s= s(p)$ is a function of the parameter.
}
\label{fig:1PR-circuit}
\end{figure} % }}}

@@

Next, we note that it is not necessary to consider rotations about an arbitrary axis,
as a rotation about any axis $\hat{n}$ parameterized by $p$
can be transformed into a rotation about $\sigma_3$ without introducing 
gates that depend on $p$. To see this, consider the rotation $R_{\hat{n}}(2s)$, where $2s$ 
is a function of $p$ (the factor of 2 is for convenience later on) 
and $\hat{n} = (n_1,n_2,n_3)$ represents the rotation axis. 
We can express $\hat{n}$ as $(\sin \theta \cos \phi, \sin \theta \sin \phi, \cos \theta)$, 
where $\theta$ and $\phi$ are fixed angles dependent on $\hat{n}$. 
The rotation can then be rewritten as follows:
\begin{eqnarray}
R_{\hat{n}}(2s) = R_{\sigma_3}(\phi) R_{\sigma_2}(\theta) R_{\sigma_3}(2s) R_{\sigma_2}(-\theta) R_{\sigma_3}(-\phi).
\end{eqnarray}
Since the angles $\theta$ and $\phi$ do not depend on the parameter $p$,
any 1PR circuit can be transformed into a circuit where the parametrized
 rotation is around $\sigma_3$ instead of an arbitrary axis. 
Moreover, without loss of generality, we can choose the last qubit as the
target qubit for the rotation, since if it weren't, we could use
swap gates to move the rotation
to the last qubit without adding gates
that depend on $p$.

Therefore, a 1PR circuit can be transformed such
that the rotation is around $\sigma_3$ and is applied to the last qubit 
(possibly controlled by other qubits), 
resulting in the form depicted in \fref{fig:1PR-circuit}. 
$\blacksquare$ \\
$\;$\\

@@

First, applying $B$ to $|j\rangle$ results in $B|j\rangle = B_{0,j} |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$,
which can be rewritten by separating the
first $N-1$ qubits from the last one as:
\begin{equation}
B|j\rangle = \sum_{k=0}^{2^{N-1}-1} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j} |k\rangle |1 \rangle \right).
\end{equation}
After the operator $B$, the circuit applies the  controlled rotation $R$.
To simplify the analysis, we separate the states of
the first $N-1$ qubits into those that fulfill the control conditions of the rotation
(which we denote as the set $\mathcal{C}$)
and those that do not, and write it as
\begin{eqnarray}
B|j\rangle = \sum_{k \in \mathcal{C}} \left(B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j} |k\rangle |1 \rangle \right) + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j}|k\rangle |1\rangle \right),
\end{eqnarray}
Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
and not the others. Therefore,  
remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is}$ to $|0\rangle$
and a phase $e^{is}$ to $|1\rangle$,
% \begin{small}
% \begin{eqnarray}
% &e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
% + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
% & \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
% \end{eqnarray}
% \end{small}
% test
\begin{align}
RB|j\rangle& = e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
+ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1}
|k\rangle |j \rangle \right) \nonumber \\
& = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
\end{align}
where $\vec{a'} = \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle$,
$\vec{b'}_j = \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle$,
$\vec{c'}_j =\sum_{k \not\in \mathcal{C}} \big( B_{2k,j} |k\rangle |0\rangle+$
$ B_{2k+1} |k\rangle |j \rangle \big)$.
\cpnote{Preferira que tuvieramos que los kets fisicos tuvieran la notacion de
ket. Intenta modificarlo asi y luego sigo con la prueba. Ya no me está pareciendo 
tan latosa. Trata tambien que los nombres que usas sean como consistentes o tengan 
algo que decir de su contenido.}
These vectors are clearly orthogonal because they are each linear combinations of different 
orthogonal states of the computational base. 
Moreover, they satisfy $|\vec{a'}_j|^2 + |\vec{b'}_j|^2 + |\vec{c'}_j|^2 = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
which is unitary.

@@

%Therefore, from this theorem we conclude that
%the kind of curves of states that can be created
%using a 1PR circuit are always of the form
%\begin{align*}
%|b(p)\rangle= e^{is} \vec{a} + e^{-is} \vec{b} + \vec{c},
%\end{align*}
%where $s$ is a function of $p$, $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors and
%$|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2 = 1$.
%%\textbf{Puntos:}
%\begin{itemize}
%\item As said before, to implement a Pauli dynamical map, 
%we need to create the parametrized $2n$-qubit state 
%$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
%\item However, creating this state will in general require many rotations parametrized by $p$. 
%For example, for the case of a Pauli dynamical map on 1 qubit, 
%the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
%In general, to create a parametrized state on $2n$ ancilla qubits will require
%$2n-1$ rotations parametrized by $p$.
%\item How can we reduce the amount of parametrized rotations used?
%\item \textbf{1PR Circuit:} Define an 1PR circuit (a circuit with one parametrized rotation)
%\item \textbf{Theorem about 1PR circuits:} \textit{An 1PR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
%\begin{eqnarray}
%U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
%\end{eqnarray}
%\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
%\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
%aunque se puede y debe achicar bastante.
%\end{itemize}
% }}}
\section{1PR circuit for a Pauli map} % {{{
\label{sec: 1PR circuit for a Pauli map}
